---
title: "p8105_hw1_zl2978"
author: Zhiye Lou
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```
##Probelm 1
Create a data frame
```{r create_df}
pro1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("q", "w", "e", "r", "y", "u", "i", "o", "p",
"a"),
    fac_vec = factor(c("good", "good", "good", "good", "fair", "fair", "fair", "fair", "bad", "bad"))
)
```
Then I will take the mean of each of my variable in pro1_df
```{r mean_of_pro1}
mean(pull(pro1_df, samp))
mean(pull(pro1_df, samp_gt_0))
mean(pull(pro1_df, char_vec))
mean(pull(pro1_df, fac_vec))
```
I can take the mean of numbers and logical vectors, but not 
character or factor.

```{r convert_numeric}
as.numeric(pull(pro1_df, samp_gt_0))
as.numeric(pull(pro1_df, char_vec))
as.numeric(pull(pro1_df, fac_vec))
```
I can take convert the logic variable and factor variable to numeric variable, but I cannot convert the character vector to numeric variable. The reason is the default value of a logical vector is 0 and 1, and thus I could convert and take the mean of a logical variable. There is no default value for the character vector, so I cannot convert or take the mean of them. Though the default value of the factor variable is{1,2,3...}, I cannot take the mean of it because the mean of the factor variable does not make sense in real world (since the difference between good and fair is not equaling the difference between bad and fair), but I could convert them to the numeric variable.


Then I will convert the logic variable to different forms and multiply the random sample
```{r mutip_logic}
as.numeric(pull(pro1_df, samp_gt_0)) * pull(pro1_df, samp)
as.factor(pull(pro1_df, samp_gt_0)) * pull(pro1_df, samp)
as.numeric(as.factor(pull(pro1_df, samp_gt_0))) * pull(pro1_df, samp)
```

##Problem 2

I will first load the penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
```

The dataset penguins has variables `r ls(penguins)`, the value of bill_depth_mm is ranged from `r min(penguins$bill_depth_mm, na.rm=TRUE)` to `r max(penguins$bill_depth_mm, na.rm=TRUE)`, the value of bill_length_mm is ranged from `r min(penguins$bill_length_mm, na.rm=TRUE)` to `r max(penguins$bill_length_mm, na.rm=TRUE)`, the body_mass_g is ranged from `r min(penguins$body_mass_g, na.rm=TRUE)` to `r max(penguins$body_mass_g, na.rm=TRUE)`, the flipper_length_mm is ranged from `r min(penguins$flipper_length_mm, na.rm=TRUE)` to `r  max(penguins$flipper_length_mm, na.rm=TRUE)`, and the year is ranged from `r min(penguins$year)` to `r max(penguins$year)`. The types of island are `r levels(penguins$island)`, the sex are `r levels(penguins$sex)`, and the types of species are `r levels(penguins$species)`. The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns, and the mean of the flipper length without missing value is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`.

Then I will draw a scatterplot of flipper_length_mm against bill_length_mm 
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm,color = species)) + geom_point(na.rm = TRUE)
ggsave("penguins_flipper_bill_plot.pdf",height = 6,width = 9)
```









